True versus apparent shapes of astrophysical bow shocks

### 2015-06-25 papers/Paper1/sec-conic.tex
25/06/15 Procedure description

\subsection{Characteristic radii}

@@

>>>>

Due to the similitudes between the parametrization of the ellipse and the hyperbola, we can do the following parametrization:

\begin{align}
x = au_c(t)-x_0 \\ 
y = bv_c(t)
\end{align}

where:
\begin{align}
u_c(t) = \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
\cosh t ~mathrm{if~hyperbola}
\end{array}\right
\end{align}\\
v_c(t) = \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~mathrm{if~hyperbola}
\end{array}\right \\
-\pi < t < \pi \\
R_0 = a - x_0 
\end{align}

@@

Once the parametrization is done, we can find the apparent shape of the shell in the observer's frame, following the procedure explained in section \ref{sec:projection}.

First of all, the intrinsic 3D shape of the shell is given by:

\begin{align}
x = au_c(t)-x_0 \\ 
y = bv_c(t)\cos\phi \\
z =  bv_c(t)\sin\phi
\end{align}

The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:tanalpha}), then:

\begin{align}
\tan\phi &= \frac{b}{a}w_c(t) 
\end{align}
where:

\begin{align}
w_c(t) = \left\lbrace \begin{array}{c}
\cot t ~\mathrm{if~ellipse} \\
-\coth t ~mathrm{if~hyperbola}
\end{array}\right
\end{align}
\subsection{Characteristic radii}
